\section{Experience}
\subsection{Instructor}{Coding Dojo}{November 2021 - present}
\begin{itemize}
\item Delivered in person and online instruction to a group of 10 to 30 students.
\item Evaluated student progress and understanding of course material.
\item Provided instruction in 
\textbf{\emph{HTML}},
\textbf{\emph{CSS}},
\textbf{\emph{JavaScript}},
\textbf{\emph{Python}},
\textbf{\emph{Flask}},
\textbf{\emph{MySQL}},
\textbf{\emph{Java}},
\textbf{\emph{Spring}},.
\end{itemize}

\subsection{Instructor}{Nucamp}{February 2020 - February 2021}
\begin{itemize}
    \item Delivered remote instruction to groups of 8 to 12 students. 
    \item Provided instruction in 
    \textbf{\emph{HTML}},
    \textbf{\emph{CSS}},
    \textbf{\emph{JavaScript}},
    \textbf{\emph{Python}},
    \textbf{\emph{React}}, and
    \textbf{\emph{Redux}},.
    \item Monitored student progress using formal and informal assessment tools both proscribed and self generated.    
\end{itemize}

\subsection{Facilitator}{Girls Who Code}{June 2019 - August 2019}
\begin{itemize}
    \item Delivered Computer Science lessons while maintaining an engaging and accessible classroom. 
    \item Managed and adapted instruction based on student proficiency with computer science concepts.
    \item Supervised a Teaching Assistant in classroom management, instruction and logistical tasks.
\end{itemize}

\subsection{Training Engineer}{Schneider National}{Aug 2013 - Jun 2015}
\begin{itemize}
    \item Maintained positive customer relationships through open lines of honest communication. 
    \item Trained new employees in safety and maintenance standards.
    \item Provided training for new employees over seven consecutive days. 
\end{itemize}

\subsection{Social Studies Teacher}{Los Angeles Unified School District}{August 2007 - June 2012}
\begin{itemize}
    \item Designed and taught curriculum for Social Science for middle and high school students 
    \item Collaborated with colleagues in other disciplines in order to incorporate STEM in the Social Science curriculum.
    \item Created and maintained discipline system in the capacity of temporary dean of students.
\end{itemize}

\subsection{Deputy Sheriff}{Los Angeles County Sheriff’s Department}{September 1999 - August 2007}
\begin{itemize}
    \item Provided law enforcement services in a variety of venues.
    \item Prepared and maintained written and digital logs and reports for law enforcement records and court proceedings.
    \item Functioned as an integral member of a criminal court staff by providing security and assisting in daily court proceedings.
\end{itemize}
% \subsection{Some Role}{Somewhere}{Aug 2021 - Jun 2022}
% \begin{itemize}
%     \item \lipsum[2][2] \emph{\lipsum[2][1]} for \textbf{\lipsum[5][1]} \lipsum[1][1] \textbf{\lipsum[4][4]} 
%     \item \lipsum[2][2] \emph{\lipsum[2][1]} for \textbf{\lipsum[5][1]} \lipsum[1][1] \textbf{\lipsum[4][4]} 
% \end{itemize}