%---- Required Packages and Functions ----

\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\footskip}{4.08003pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.0cm, top=1cm, right=1cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\

        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Tyler Maxwell} % Your Name
\newcommand{\phone}{818-809-0653}
\newcommand{\emaila}{tmax818@mac.com}



\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------


\parbox{\dimexpr\linewidth-0.3cm\relax}{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} \\ 
  {\raisebox{0.0\height}{\footnotesize \faPhone}\ \phone} & \href{https://github.com/tmax818}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}}\\
  \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize 
 \faEnvelope}\ {\emaila}}&\href{https://www.linkedin.com/in/tylermaxwell/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
\end{tabularx}
}


\section{\textbf{Professional Summary}}

Experienced educator and web development instructor with a strong background in computer science and education. Proven ability to design and deliver engaging curriculum, foster student development, and maintain a positive learning environments and outcomes. Skilled in various programming languages and technologies, with a passion for continuous learning and professional growth. Dedicated to making a meaningful impact through education and community service.

%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University}{GPA: 3.95}
      {Single-Subject Teaching Credential (Social Science and General Science)}{2010}
    \resumeSubheading
      {University of California, Los Angeles}{GPA: 2.76}
      {BA Philosophy}{2001}
%   \resumeSubheading
%       {Your School name}{CGPA/Percentage: xxx}
%       {Board of Secondary Education, State}{Year}
  \resumeSubHeadingListEnd
% \vspace{-5.5mm}\href{https://github.com/tmax818}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}}
%

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Coding Dojo}{Bellevue, WA}
      {Web Development Instructor}{January 2021 - May 2024}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Delivered in-person and on-line instruction to a group of 10 to 30 students in full stack web development.}
    \item {Evaluated student progress and understanding, providing tailored feedback and guidance on coursework and assignments.}
    \item {Developed and maintained curriculum and instructional materials, ensuring up-to-date content and industry relevance.}
    \item {Collaborated with fellow instructors to enhance teaching strategies and share best practices.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
    
    \resumeSubheading
      {Nucamp Coding Boot Camp}{Bellevue, WA}
      {React and Python Instructor}{February 2020 - February 2022}
      \vspace{-1.0mm}
      \resumeItemListStart
    \item {Conducted interactive online classes via Zoom, teaching web development and Python fundamentals to groups of 8-12 students.}
    \item {Managed and adapted instruction based on student progress, ensuring mastery of React and Redux concepts.}
    \item {Mentored students through coding projects, fostering problem-solving skills and project management.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
    
    \resumeSubheading
    {Girls Who Code}{Burbank, CA}
    {Summer Immersion Program Instructor}{May 2019 - August 2019}
    \vspace{-2.0mm}
    \resumeItemListStart
    \item {Delivered engaging Computer Science lessons, maintaining an inclusive and dynamic classroom environment.}
    \item {Coordinated with a Teaching Assistant to manage classroom logistics and provide individualized student support.}
    \item {Developed activities and projects that encouraged creativity and practical application of coding skills.}
    \resumeItemListEnd
    
    \vspace{-3.0mm}
    
    \resumeSubheading
      {Los Angeles Unified School District}{Los Angeles}
      {Teacher}{August 2007 - August 2012}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Designed and presented comprehensive Social Science curriculum for middle school students, promoting critical thinking and historical analysis.}
    \item {Successfully integrated technology into the classroom to enhance learning experiences.}
    \item {Held leadership roles in both district and charter institutions, contributing to curriculum development and school improvement initiatives.}
    \resumeItemListEnd
    
 
    \vspace{-3.0mm}
    
    \resumeSubheading
      {Los Angeles County Sheriff's Department}{Los Angeles}
      {Deputy Sheriff}{September 1999 - August 2007}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Provided law enforcement services across various venues, ensuring community safety and legal compliance.}
    \item {Prepared and maintained detailed logs and reports for law enforcement records and court proceedings.}
    \item {Engaged in community outreach programs, fostering positive relationships and trust with the public.}
    \resumeItemListEnd
    
 
    
    % \vspace{-3.0mm}

    % \resumeSubheading
    %   {Company Name}{City}
    %   {Your Role}{Event dates}
    %   \vspace{-2.0mm}
    %   \resumeItemListStart
    % \item {Work description line 1}
    % \item {Work description line 2}
    % \resumeItemListEnd


  \resumeSubHeadingListEnd

\vspace{-7.25mm}

%-----------PROJECTS-----------------
\section{\textbf{Technical Projects}}
\resumeSubHeadingListStart


\resumeProject
      {\href{https://www.tylermaxwell.co/}{\raisebox{0.0\height}{\footnotesize }\ {Personal Website}}} %Project Name
      {Personal portfolio website} %Project Name, Location Name
      {2018} %Event Dates

      \resumeItemListStart
        \item {Tools \& technologies used: HTML, CSS, Ruby, Jekyll}
        \item {Developed a personal portfolio website showcasing my projects and skills.}
        \item {Utilized custom SASS and CSS for a modern and responsive front-end design.}
      \resumeItemListEnd

    \vspace{-2.0mm}
    
  \resumeProject
      {\href{https://www.tylermaxwell.co/python_april/}{\raisebox{0.0\height}{\footnotesize }\ {Python Presentation Website}}} %Project Name
      {Website reference for students in my Python class.} %Project Name, Location Name
      {2023} %Event Dates

      \resumeItemListStart
        \item {Tools \& technologies used: HTML,CSS, JavaScript, NPM, Reveal.js}
        \item {Created an interactive website for students in my Python class to reference course materials and resources.}
        \item {Enhanced user experience with dynamic presentations and organized content delivery.}
      \resumeItemListEnd
    

  %   \vspace{-2.0mm}
    
  % \resumeProject
  %     {Project Name} %Project Name
  %     {Project description(Your input in the project)} %Project Name, Location Name
  %     {Event dates} %Event Dates

  %     \resumeItemListStart
  %       \item {Tools \& technologies used: xxx,xxx}
  %       \item {More description on the project(The output you achieved by working on the project)}
  %     \resumeItemListEnd
    

    
      
  \resumeSubHeadingListEnd
\vspace{-5.5mm}



%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Technical Skills}{: HTML, CSS, JavaScript, Python, Ruby, Java, Elisp, C/C++} \\
     \textbf{Soft Skills}{:Training, Education, Writing, Editing, Communication, Problem-Solving } \\
     \textbf{Field of Interest}{: Computer Science, Mathematics, Chemistry, Physics, Science Education } \\
     \textbf{Hobbies}{: Reading, Electronics, Programming, Life-long Learning, Making} \\
    }}
 \end{itemize}
 \vspace{-16pt}



% %-----------Positions of Responsibility-----------------
% \section{\textbf{Positions of Responsibility}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Position, } % Position
%     {Club or Event} %Club,Event
%     {Position tenure} %Tenure Period
%     -work description in 1 line
% \resumePOR{Position, } % Position
%     {Club or Event} %Club,Event
%     {Position tenure} %Tenure Period
% -work description in 1 line
    
% \resumeSubHeadingListEnd
% \vspace{-5mm}




%-----------Achievements-----------------
\section{\textbf{Certifications}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Full Stack Web Development Certification } % Award
    {Flatiron School } % Event
    {2018} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year


\resumeSubHeadingListEnd
\vspace{-5mm}



%-------------------------------------------
\end{document}